|

### 2021-12-15 front-and-back-matter/99-appendices.Rmd
Typo in appendix

(ref:searchHitsMedline-caption) __Medline search strategy__ - Full list of search terms used to identify relevant records in the Medline bibliographic database. The number of records returned per search term is also displayed.

(ref:searchHitsMedline-scaption) Medline search strategy

>>>>

(ref:searchHitsMedline-caption) __MEDLINE search strategy__ - Full list of search terms used to identify relevant records in the MEDLINE bibliographic database. The number of records returned per search term is also displayed.

(ref:searchHitsMedline-scaption) MEDLINE search strategy
